Agile Monitoring of Evolving Web Services: For the Little Man

### 2018-04-07 utilization.tex
stupid footnote removed.

  The default landing page of the dashboard presents an overview of all the endpoints, 
  which presents some basic utilization information as:
  (1) the number of calls to that endpoint since the begining of tracking
  (2) the number of calls in the last seven days, and
  (3) the number of calls in the last day\footnote{Although very useful, it was only after several months of using the system that the client requested the extra columsn for one day and seven days. An argument for slow research}s
  \va{Please remove the last footnote - it's the equivalent of shooting yourself in the leg.}

>>>>

  The default landing page of the dashboard presents an overview of all the endpoints, 
  which presents some basic utilization information as:
  (1) the number of calls to that endpoint since the begining of tracking
  (2) the number of calls in the last seven days, and
  (3) the number of calls in the last day
